### 2019-11-20 thesis/txt/1-related-work.tex
rework TOC with latest Feedback from Moritz, replace log screenshots

\chapter{Background}
\plan{whole RW currently highly work in progress, text not yet coherent!}
\plan{all of RW: 4 - 5 pages left to do + some research!}
\plan{write, 1/3 page, blocked by: other sections}
\label{sec:rw}
This section presents various research works adjacent or foundational to our work.
Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation.
We differentiate our work from the more common system log analysis and show how we classify build logs as semi-structured data.
We cover different information retrieval and extraction techniques \todo{half sentence missing: specify which techniques? 'used in software reasearch' 'used to assist software engineers'}.
Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.
\todo{do we also mention more things?}
% moritz: nice formulation :)

\section{Continuous Integration}
This section starts with an overview on research into why CI is used and its impact on development.
It presents analyses on why CI builds fail and how testing and static anlysis tools are used within CI.
We explain how researchers compose data sets for their work on CI and how chunk retrieval techniques can support them.

\paragraph{Motivation for CI and impact of CI}
Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
Developers use CI to ensure consistency and quality across different execution environments and increase confidence into the code they deploy.
Hilton et al.~\cite{hilton2016usage} also analyze how and why open source projects use CI.
They observe CI usage in a broad range of projects, it supports them to catch bugs earlier and have more confidence in a successful build and shorten release cycles.
Stahl and Bosch~\cite{staahl2014modeling} provide a hollistic review of literature on automatic build environments in industry projects.
They propose a descriptive structure to model build flows, which they found to be highly different from project to project.
Vasilescu et al.~\cite{vasilescu2015quality} analyzed a broad rage of open source projects written in popular languages on GitHub.
They compared their usage of CI with the successful merges of pull requests and found that CI increase the number of successful merges, internal as well as external contributions, and allows the team members to uncover more bugs.
In a new study, Vasallo et al.~\cite{vassallo2019every} interview developers on how they determine why a CI build failed.
They model how these developers resolve failures.
The first and most important steps when developers want to fix a build failure is locating the error within the build log.
Then the developers use the additional information provided with and around the error message to understand the details of the failures.
% Vassallo et al.~\cite{vassallo2018continuous} conducted a survey study on how ci influences developers to continuously refactor their code to fix ci quality analysis warnings.
% Their results indicate that refactoring is rather spread in the ci environment and deemed important by the surveyed developers.
% ``Lack of time'' and ``absence of a proper test suite'' are named as the main barriers to continuous refactoring.
% Vassallo et al.~\cite{vassallo2019automated} analyzed build logs, source code repository content and build metadata of open source repositories for CI anti-patterns.

@@

\paragraph{Data Sets powering CI Research}
The works presented in this section are based on either developer surveys or data sets, containing build metadata or build logs.
Seo et al..~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
Beller et al. created the \emph{TravisTorrent} data set~\cite{beller2017travistorrent} providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
TravisTorrent was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
They also identify cascading build failures created by existing unfixed errors and allowed failures, whose results were later labeled by developers to be ignored.
About half of the failed builds in \emph{TravisTorrent} fall into at least one of these categories.
When regarded as noise they considerably impact observations reported by other works modeling build breakages.

@@

\section{Build Log Analysis and Augmentation - Related Work}
\label{sec:rw-bl-analysis}
Build logs are a valuable data source for developers to find out why their build failed.
Various researchers are looking into supporting developers to process the verbose build logs.
Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
The hint generators leverage this structured access to the information within the build log to propose fixes.
One of the hint generators for example queries stack overflow for discussions related to why the build failed.
In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
The chunk retrieval techniques we compare in this thesis can be used to fill similar structured representations with information from build logs.
As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, the main influence factor on the structure of a build log.

@@

\section{System Log Analysis}

A related field of log processing is the processing of system log files produced during runtime.
A main difference in system logs is that they are fundamentally structured through events.
Each line in the log file represents one event.
The first goal in parsing system log files is to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
Next the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
The output of a log parser is a structured log, composed of a list of timed events and the corresponding parameter values~\cite{he2016evaluation}.
This structured log is then the input to various machine learning and data mining processes.
They mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
Xu et al.~\cite{xu2009detecting} leveraged the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.

Classic log parsers interpret the whole log file into a sequence of events.
A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
In this thesis we taka a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g. through regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.

\section{Semi-Structured Data}
\label{sec:rw-semi-structured-data}
Serge Abiteboul introduced a theory of semi-structured data in his report from 1997 about integrating data from several sources~\cite{abiteboul1997querying}.
He proposes essential characteristics of semi-structured data, and we show how five of these map to the context of build logs.

@@

\section{Information Extraction and Retrieval Techniques}

@@

\paragraph{Information Extraction from Semi-Structured Documents}
\emph{Information extraction} techniques aim at structuring unstructured information to support subsequent processing.

The PADS project~\cite{fisher2011the-pads} is centered around declaring grammars for the information contained in semi-structured documents.
Based on this declarative data description various tools are generated like format converters, e.g. to XML, data adaptors to other tools, statistical analyzers and visualizers.
Manually defined PADS grammars eliminate the need to develop a custom data extraction parser.
Xi and Walker developed ANNE~\cite{xi2010a-context-free}, which can infer context-free PADS grammars from a small number of user annotations and the raw document data.
Fisher et al.~\cite{fisher2008from} fully automated the generation of PADS grammars.
They split the data into chunks, lines or documents, and further into tokens.
Parentheses are used to infer hierarchical structure information.
The system guesses grammar operators unifying single tokens or subexpressions, scores the resulting grammars and applies appropriate rewrite rules to refine the candidate grammars.

@@

\paragraph{Information Retrieval in Software Engineering Research}
The process of automatically selecting unstructured documents related to a given \emph{search query} is called \emph{information retrieval}~\cite{schutze2008introduction}.

@@

\section{Program Synthesis by Example}
\label{sec:rw-prose}
Programming by Example enables end users to automate repetitive tasks.
The user provides examples for the input and the corresponding output and a synthesis algorithm tries to create the program intended by the user.
This section introduces the theoretical foundations of the program synthesis algorithm of the \emph{Program Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
The PROSE framework is developed by Microsoft Research.
The section next presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
Further, we cover additional applications and extensions of the PROSE program synthesis and alternative research on generating regular expressions from examples.

@@

\paragraph{User Interaction with Programming by Example}
I/O examples are an ambiguous specification of a program and user confidence in the correctness of the synthesized program is important for a wide adoption of Programming by Example based systems~\cite{lau2009why-programming-by-demonstration}.
Miller and Myers~\cite{miller2001outlier} uncover outliers in input data provided to a Programming by Example text editing task.
For the PROSE framework, Mayer et al.~\cite{mayer2015user} compare two approaches for disambiguation by the user.
With their first approach, the user can browse lower ranked program candidates in a tree like natural language transformation of the constructed VSA.
The second approach actively asks the user to resolve ambiguous output possibilities for input only examples.

>>>>

\chapter{Background and Related Work}
\label{sec:rw}
This section presents various research works adjacent or foundational to our work.
To start, we describe studies about continuous integration (CI) and how they gather information about CI usage in software projects.
Next, the section moves on to works about build log analysis and their augmentation, which are related to the techniques we analyze in this thesis.
We differentiate our work from system log analysis and show how we classify build logs as semi-structured data.
The section describes how chunk retrieval can be employed as a part of presented information extraction approaches.
We introduce how information retrieval techniques, the basis for CTS, are used to improve software development.
Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library, the foundation of PBE\@.
% moritz: nice formulation :)

\section{Continuous Integration and Build Logs}
\subsection{Continuous Integration}
This section starts with an overview on research into why CI is used and its impact on development.
It presents analyses on why CI builds fail and how testing and static analysis tools are used within CI\@.
We explain how researchers compose data sets for their work on CI and how chunk retrieval techniques can support them.

\paragraph{Motivation for CI and Impact of CI}
Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
Developers use CI to ensure consistency and quality across different execution environments and increase confidence into the code they deploy.
Hilton et al.~\cite{hilton2016usage} also analyze how and why open source projects use CI\@.
They observe CI usage in a broad range of projects, it supports them to catch bugs earlier and have more confidence in a successful build and shorten release cycles.
Stahl and Bosch~\cite{staahl2014modeling} provide a holistic review of literature on automatic build environments in industry projects.
They propose a descriptive structure to model build flows, which they found to be highly different from project to project.
Vasilescu et al.~\cite{vasilescu2015quality} analyzed a broad rage of open source projects written in popular languages on GitHub.
They compared their usage of CI with the successful merges of pull requests and found that CI increase the number of successful merges, internal as well as external contributions, and allows the team members to uncover more bugs.
In a new study, Vasallo et al.~\cite{vassallo2019every} interview developers on how they determine why a CI build failed.
They model how these developers resolve failures.
The first and most important steps when developers want to fix a build failure is locating the error within the build log.
Then the developers use the additional information provided with and around the error message to understand the details of the failures.
% Vassallo et al.~\cite{vassallo2018continuous} conducted a survey study on how ci influences developers to continuously refactor their code to fix ci quality analysis warnings.
% Their results indicate that refactoring is rather spread in the ci environment and deemed important by the surveyed developers.
% ``Lack of time'' and ``absence of a proper test suite'' are named as the main barriers to continuous refactoring.
% Vassallo et al.~\cite{vassallo2019automated} analyzed build logs, source code repository content and build metadata of open source repositories for CI anti-patterns.

@@

\paragraph{Data Sets Powering CI Research}
The works presented in this section are based on either developer surveys or data sets, containing build metadata or build logs.
Seo et al..~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
Beller et al.\ created the \emph{TravisTorrent} data set~\cite{beller2017travistorrent} providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
TravisTorrent was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
They also identify cascading build failures created by existing unfixed errors and allowed failures, whose results were later labeled by developers to be ignored.
About half of the failed builds in \emph{TravisTorrent} fall into at least one of these categories.
When regarded as noise they considerably impact observations reported by other works modeling build breakages.

@@

\subsection{Augmentation of Build Logs}
\label{sec:rw-bl-analysis}
Build logs are a valuable data source for developers to find out why their build failed.
Various researchers are looking into supporting developers to process the verbose build logs.
Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
The hint generators leverage this structured access to the information within the build log to propose fixes.
One of the hint generators for example queries stack overflow for discussions related to why the build failed.
In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
The chunk retrieval techniques we compare in this thesis can be used to fill similar structured representations with information from build logs.
As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, the main influence factor on the structure of a build log.

@@

\subsection{Build Logs as Semi-Structured Data}
\label{sec:rw-semi-structured-data}
Serge Abiteboul introduced a theory of semi-structured data in his report from 1997 about integrating data from several sources~\cite{abiteboul1997querying}.
He proposes essential characteristics of semi-structured data, and we show how five of these map to the context of build logs.

@@

\subsection{System Log Analysis}
\label{sec:log-analysis}
A related field of log processing is the processing of system log files produced during runtime.
A main difference in system logs is that they are fundamentally structured through events.
Each line in the log file represents one event.
The first goal in parsing system log files is to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
Next the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
The output of a log parser is a structured log, composed of a list of timed events and the corresponding parameter values~\cite{he2016evaluation}.
This structured log is then the input to various machine learning and data mining processes.
They mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
Xu et al.~\cite{xu2009detecting} leveraged the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.

Classic log parsers interpret the whole log file into a sequence of events.
A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
In this thesis we taka a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ through regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.

\section{Foundational Techniques}
% \section{Information Extraction and Retrieval Techniques}

@@

\subsection{Information Extraction} %from Semi-Structured Documents
\emph{Information extraction} techniques aim at structuring unstructured information to support subsequent processing.

The PADS project~\cite{fisher2011the-pads} is centered around declaring grammars for the information contained in semi-structured documents.
Based on this declarative data description various tools are generated like format converters, e.g.\ to XML, data adaptors to other tools, statistical analyzers and visualizers.
Manually defined PADS grammars eliminate the need to develop a custom data extraction parser.
Xi and Walker developed ANNE~\cite{xi2010a-context-free}, which can infer context-free PADS grammars from a few user annotations and the raw document data.
Fisher et al.~\cite{fisher2008from} fully automated the generation of PADS grammars.
They split the data into chunks, lines or documents, and further into tokens.
Parentheses are used to infer hierarchical structure information.
The system guesses grammar operators unifying single tokens or subexpressions, scores the resulting grammars and applies appropriate rewrite rules to refine the candidate grammars.

@@

\subsection{Information Retrieval}% in Software Engineering Research
The process of automatically selecting unstructured documents related to a given \emph{search query} is called \emph{information retrieval}~\cite{schutze2008introduction}.

@@

\subsection{Program Synthesis by Example}
\label{sec:rw-prose}
Programming by Example enables end users to automate repetitive tasks.
The user provides examples for the input and the corresponding output and a synthesis algorithm tries to create the program intended by the user.
This section introduces the theoretical foundations of the program synthesis algorithm of the \emph{Program Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
The PROSE framework is developed by Microsoft Research.
The section next presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
Further, we cover additional applications and extensions of the PROSE program synthesis and alternative research on generating regular expressions from examples.

@@

\paragraph{User Interaction with Programming by Example}
I/O examples are an ambiguous specification of a program and user confidence in the correctness of the synthesized program is important for a wide adoption of Programming by Example based systems~\cite{lau2009why-programming-by-demonstration}.
Miller and Myers~\cite{miller2001outlier} uncover outliers in input data provided to a Programming by Example text editing task.
For the PROSE framework, Mayer et al.~\cite{mayer2015user} compare two approaches for disambiguation by the user.
With their first approach, the user can browse lower ranked program candidates in a tree like natural language transformation of the constructed VSA\@.
The second approach actively asks the user to resolve ambiguous output possibilities for input only examples.

### 2019-11-20 thesis/txt/2-models.tex
rework TOC with latest Feedback from Moritz, replace log screenshots

\chapter{Introduction to Chunk Retrieval Techniques}
\label{sec:techniques}
This chapter introduces the concept of chunk retrieval techniques.
We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
This chapter first presents how a build log, the input to our chunk retrieval, is created by a continuous integration (CI) build.
Next, it describes retrievable information chunks in build logs and gives examples found in Travis CI build logs.
We illustrate why it is useful to extract the presented information chunks.
The following section introduces our concept of chunk retrieval techniques, which retrieve information chunks from build logs.
We present the three chunk retrieval techniques we investigate for this thesis:
Program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).

@@

	\item \textbf{ExitCode} Travis CI prints all exit codes of commands.
				A researcher can retrieve this information to fill an overview of the build steps and why they failed.
	      Figure~\ref{fig:log-3} shows an example of an ExitCode instantiation within a build log.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log0.png}
	\caption{Excerpt from a build log showing textual representations of a long TravisWorker instantiation and a TravisSystemInfo instantiation}
	\label{fig:log-0}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log1.png}
	\caption{Excerpt from a build log showing textual representations of a TravisTiming instantiation and a TravisPhase, containing the TravisPhaseName and the TravisPhaseOutput}
	\label{fig:log-1}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log2.png}
	\caption{Excerpt from a build log showing textual representations of a short TravisWorker instantiation}
	\label{fig:log-2}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log3.png}
	\caption{Excerpt from a build log showing textual representations of ErrorMessage, ExitCode and TravisTriggeringCommand instantiations}
	\label{fig:log-3}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log4.png}
	\caption{Excerpt from a build log showing textual representations of WarningMessage instantiations}
	\label{fig:log-4}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log5.png}
	\caption{Excerpt from a build log showing textual representations of WarningMessage instantiations}
	\label{fig:log-5}
\end{figure}

@@

\subsection{Other Techniques}
\label{sec:expl-rlr}
Apart from the three techniques we investigate, there are further build log analysis techniques mentioned in literature and used in industry.
This section shows how they are described with our notion of chunk retrieval techniques.

>>>>

\chapter{Chunk Retrieval Techniques for Build Logs}
\label{sec:techniques}
This chapter introduces the concept of chunk retrieval techniques.
We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
This chapter first presents how a build log, the input to our chunk retrieval, is created by a continuous integration (CI) build.
Next, it describes retrievable information chunks in build logs and gives examples found in Travis CI build logs.
We illustrate why it is useful to extract the presented information chunks.
The following section introduces our concept of chunk retrieval techniques, which retrieve information chunks from build logs.
We present the three chunk retrieval techniques we investigate for this thesis:
Program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).

@@

	\item \textbf{TravisExitCode} Travis CI prints all exit codes of commands.
				A researcher can retrieve this information to fill an overview of the build steps and why they failed.
	      Figure~\ref{fig:log-3} shows an example of an TravisExitCode instantiation within a build log.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log02.png}
	\caption{Excerpt from a build log showing textual representations of a long TravisWorker instantiation and a TravisSystemInfo}
	\label{fig:log-0}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log12.png}
	\caption{Excerpt from a build log showing textual representations of a TravisTiming and a TravisPhase, containing the TravisPhaseName and the TravisPhaseOutput}
	\label{fig:log-1}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log22.png}
	\caption{Excerpt from a build log showing the textual representation of a short TravisWorker}
	\label{fig:log-2}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log32.png}
	\caption{Excerpt from a build log showing textual representations of an ErrorMessage, an ExitCode and a TravisTriggeringCommand}
	\label{fig:log-3}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log42.png}
	\caption{Excerpt from a build log showing the textual representation of a WarningMessage}
	\label{fig:log-4}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/log52.png}
	\caption{Excerpt from a build log showing the textual representation of another WarningMessage}
	\label{fig:log-5}
\end{figure}

@@

\subsection{Other Techniques}
\label{sec:expl-rlr}
There are further build log analysis techniques mentioned in literature and used in industry.
This section shows how they are described with our notion of chunk retrieval techniques.

### 2019-11-20 thesis/txt/3-data-set.tex
rework TOC with latest Feedback from Moritz, replace log screenshots

\chapter{LogChunks Data Set}
\includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}

\label{sec:data-set}
\section{Motivation}
originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how structured or unstructured they are.
Then labeling of one build log information, namely the reason the build failed, as well as keywords and structural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results

@@

\subsection{Repository Sampling}
Our first task was to determine a set of repositories to query logs from.
Our \texttt{GHTorrentParser} can query the GHTorrent~\cite{gousios2013ghtorrent} data set for the most popular languages on github and the most popular repositories for a given language.
\emph{Popularity} in this case is defined as the number of watches.
Our \texttt{TravisRequester} can then check for a given repository whether it uses Travis CI.

\subsection{Build Sampling}
The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, to obtain the newest builds for a given repository.
As most builds on Travis CI are successful \mention{citation needed} we use a stratified sampling approach: \texttt{TravisRequester} saves the found builds in logs in buckets according to their state.
We encountered the following states during our data collection passes:
\begin{itemize}
	\item \todo{fill /5 mins/}
\end{itemize}
\texttt{TravisRequester} saves up to a configured number of builds per state and searches through a configured number of maximum checked builds.

\subsection{Log Sampling}
For each build the \texttt{TravisRequester} then selects a log to download.
Logs in Travis CI are not directly attributed to \texttt{build}s, but to \texttt{job}s.
A single build can consist of multiple jobs, e.g.\ building and executing tests in various different testing environments.
\texttt{TravisRequester} therefore queries each build for a job, which has the same state.
A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
For the selected jobs, our tool then queries the Travis API V3 and obtains the respective build log.

@@

\section{Data Structure}
For our study, described in Chapter~\ref{sec:study}, we want to investigate the retrieval capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

@@

\section{Labeling}
\subsection*{Output Examples: Build Failure Reason}
We labeled the first occuring substring describing the failure.
If there were multiple errors described we took the first continuous block of error description.

@@

\subsection{Inter-Rater Reliability}
re-labeling of parts of the labels - cohen's kappa
\subsubsection{Introduction}
After the manual labeling of the data set we performed a second labeling of a sample of the build logs to validate the labels.
\subsubsection{Method}
For each label category: Build Failure Reason, keywords and category, we relabeled 30 randomly sampled logs.
compared the labeles, \todo{discussed about it}.
\subsubsection{Results}

>>>>

\chapter{LogChunks Data Set}
\label{sec:data-set}
\includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}

originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how structured or unstructured they are.
Then labeling of one build log information, namely the reason the build failed, as well as keywords and structural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results

@@

\paragraph{Repository Sampling}
Our first task was to determine a set of repositories to query logs from.
Our \texttt{GHTorrentParser} can query the GHTorrent~\cite{gousios2013ghtorrent} data set for the most popular languages on github and the most popular repositories for a given language.
\emph{Popularity} in this case is defined as the number of watches.
Our \texttt{TravisRequester} can then check for a given repository whether it uses Travis CI.

\paragraph{Build Sampling}
The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, to obtain the newest builds for a given repository.
As most builds on Travis CI are successful \mention{citation needed} we use a stratified sampling approach: \texttt{TravisRequester} saves the found builds in logs in buckets according to their state.
We encountered the following states during our data collection passes:
\begin{itemize}
	\item \todo{fill /5 mins/}~\cite{travis2009buildstatus}
\end{itemize}
\texttt{TravisRequester} saves up to a configured number of builds per state and searches through a configured number of maximum checked builds.

\paragraph{Log Sampling}
For each build the \texttt{TravisRequester} then selects a log to download.
Logs in Travis CI are not directly attributed to \texttt{build}s, but to \texttt{job}s.
A single build can consist of multiple jobs, e.g.\ building and executing tests in various different testing environments.
\texttt{TravisRequester} therefore queries each build for a job, which has the same state.
A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
For the selected jobs, our tool then queries the Travis API V3 and obtains the respective build log.

@@

\section{Data Schema}
For our study, described in Chapter~\ref{sec:study}, we want to investigate the retrieval capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

@@

\section{Labeling Process}
\paragraph{Output Examples: Build Failure Reason}
We labeled the first occuring substring describing the failure.
If there were multiple errors described we took the first continuous block of error description.

@@

\subsection{Inter-Rater Reliability Study}
re-labeling of parts of the labels - cohen's kappa
\subsubsection{Introduction}
After the manual labeling of the data set we performed a second labeling of a sample of the build logs to validate the labels.
\subsubsection{Method}
For each label category: Build Failure Reason, keywords and category, we relabeled 30 randomly sampled logs.
compared the labels, \todo{discussed about it}.
\subsubsection{Results}

### 2019-11-20 thesis/txt/5-study.tex
rework TOC with latest Feedback from Moritz, replace log screenshots

\chapter{Empirical Comparison Study}
\label{sec:study}
To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{LogChunks} data set.
This chapter describes our study design and presents the results of the study.
The analysis of the study results first focusses on each of the three techniques and later we compare them against each other.

@@

\subsection{Comparing All Techniques}
Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval of the different techniques in our study.
CTS and KWS extract at least some of the desired lines in 79\% and 88.5\%.
With 38.25\%, KWS also has the highest number of successful extractions, followed by PBE with 34.5\%.
PBE has the lowest number of partial extraction with only 18 out of 400 chunk retrieval runs.

>>>>

\chapter{Empirical Comparison}
\label{sec:study}
To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{LogChunks} data set.
This chapter describes our study design and presents the results of the study.
The analysis of the study results first focusses on each of the three techniques and later we compare them against each other.

@@

\subsection{Comparison of All Techniques}
Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval of the different techniques in our study.
CTS and KWS extract at least some of the desired lines in 79\% and 88.5\%.
With 38.25\%, KWS also has the highest number of successful extractions, followed by PBE with 34.5\%.
PBE has the lowest number of partial extraction with only 18 out of 400 chunk retrieval runs.
